---
title: "Simulation of Financial Contagion"
output: html_notebook
---

The objective of the simulation is to investigate how the financial contagion depends on integration, organization diversification, portfolio diversification, and fire-sale effect with different default thresholds. Adapted from Elliott et al. (2014), the simulation incorporate another contagion channel by adding the fire-sale (liquidation) effect as an additional bankruptcy cost.

The detailed setup is as follows:

1. The numbers of assets and organizations (banks) are 100 with each organization having initial wealth of 100, and asset having initial price at 1.
2. The integration, organization diversification and portfolio diversification (represented by `c`, `d` and `e` respectively) take the grid from 1 to 20 with 1/3 as an increment.
3. The price impact parameter, `alpha`, takes six values from 0 to 1.0536 to represent different levels of price impact when assets are liquidated.
4. The default threshold, theta, varies from 0.8 to 0.99 with 0.01 as an increment.
5. For every combination of parameters, simulation is performed on 100 iterations (with few exception of 1000 or more iterations to have better accuracy)

The main results are stored in two lists: `Elliott` and `Mixed`. Each contains five arrays: average failures (`AvFailures`), probability of first failure (`AvFirstFailures`), probability of contagion (`AvSomeFailures`), the number of contagion waves (`AvNumWave`), and the number of failed organization in the first wave (`AvFirstWaveset`). With the dimension of (9, 60, 60, 6, 20), the arrays keep the final result for each combination of parameters.


# Setup
```{r}
n <- 100
m <- 100
iteration <- 100

c_range <- seq(0.1, 0.9, 0.1)
d_range <- seq(1/3, 20, 1/3)
e_range <- seq(1/3, 20, 1/3)
alpha_range <- c(0, 0.1005, 0.3046, 0.5129, 0.7257, 1.0536)
theta_range <- seq(0.8, 0.99, 0.01)

zero <- matrix(nrow=length(c_range), ncol=length(d_range))
hero <- array(data=zero, dim=c(length(c_range), length(d_range), length(e_range), length(alpha_range), length(theta_range)))

Elliott <- list(hero, hero, hero, hero, hero)
names(Elliott) <- c("AvFailures", "AvFirstFailures", "AvSomeFailures", "AvNumWave", "AvFirstWaveset")

Mixed <- list(hero, hero, hero, hero, hero)
names(Mixed) <- c("AvFailures", "AvFirstFailures", "AvSomeFailures", "AvNumWave", "AvFirstWaveset")
```


# Main Simulation
```{r}
c_counter <- 0
for (c in c_range){
  c_counter <- c_counter + 1
  
  d_counter <- 0
	for (d in d_range){
    d_counter <- d_counter + 1
    
    e_counter <- 0
    for (e in e_range){
      e_counter <- e_counter + 1
      
      alpha_counter <- 0
    for (alpha in alpha_range){
      alpha_counter <- alpha_counter + 1
      
      theta_counter <- 0
      for (theta in theta_range){
        theta_counter <- theta_counter + 1
        
        FirstFailures1 <- 0
        SomeFailures1 <- 0
        NumWave1 <- 0
        FirstWaveset1 <- 0
        TotFailures1 <- 0
    
        FirstFailures3 <- 0
        SomeFailures3 <- 0
        NumWave3 <- 0
        FirstWaveset3 <- 0
        TotFailures3 <- 0
        
        
        for (iter in 1:iteration){
          
          #A construction
          U <- matrix(runif(n*n),nrow=n,ncol=n)
          t <- d/(n-1)
          G <- ((U<t)*1)*(matrix(rep(1,n*n),nrow=n,ncol=n)-diag(n))
          
          colSumG <- colSums(G)
          colSumG <- colSumG + (colSumG==0)*1
          
          #Make it column stochastic
          L <- t(t(G)*(1/colSumG))
          
          #Compute dependency matrix
          C <- c*L + (1-c)*diag(n)
          hatC <- C*diag(n)
          A <- hatC%*%(solve(diag(n)-C+hatC))
          
          #D construction
          tmp <- matrix((runif(m*n)<e/n)*1,nrow=m)
          for (i in 1:m){
            if (sum(tmp[i,])==0){
              tmp2 <- rep(0,m)
              tmp2[sample(1:n, 1, replace=TRUE)] <- 1
              tmp[i,] <- tmp2
             }
          }
          D <- tmp/rowSums(tmp)*100
          
          
          # Elliott-------------------------------------------------------------------------------
          pold <- matrix(rep(1,n),nrow=n,ncol=1)
          underlinev <- (A%*%pold)*theta
          p <- pold
          p[1] <- 0
          fcount <- 0
          v <- A%*%p
          wset <- seq(1,100)[c((v<=underlinev)*1)==1]
          
          while (any(p!=pold)){
            
            fcount <- fcount + 1
            v <- A%*%p
  					pold <- p
  					p <- p*(v>underlinev)*1
          
          }
          
          numberOfFailures1 <- sum(v <= underlinev)
          
          FirstFailures1 <- FirstFailures1 + (fcount >= 1)*1
          SomeFailures1 <- SomeFailures1 + (fcount >= 2)*1
          NumWave1 <- NumWave1 + fcount
          FirstWaveset1 <- FirstWaveset1 + length(wset)
          TotFailures1 <- TotFailures1 + numberOfFailures1

          # Mixed-------------------------------------------------------------------------------
          
          p <- rep(1, n)
          v <- rep(100, m)
          
          total_assets <- colSums(D)
          for (i in 1:m){
            if (total_assets[i]==0){
               total_assets[i] <- 1
            }
          }
          
          underlinev <- (A%*%D%*%p)*theta
          
          # Single random asset shock (It's guaranteed to hit the one held by at least one organization)
          seeds <- subset((total_assets>0)*1:100, (total_assets>0)*1:100!=0)
          seed <- sample(seeds,1)
          
          p[seed] <- 0
          v <- A%*%D%*%p
          wset <- seq(1,100)[c((v<=underlinev)*1)==1]
          Dnew <- diag(c((v>underlinev)*1))%*%D
          
         
          liquidation <- 0
          fcount <- 0
          while (any(Dnew!=D)){
            
            fcount <- fcount + 1
            liquidation <- liquidation + colSums(D - Dnew)
            port <- liquidation/total_assets
            
            pnew <- p*exp(-alpha*port)
            v <- A%*%Dnew%*%pnew
            
    				D <- Dnew
    				Dnew <- diag(c((v>underlinev)*1))%*%D

         }
       
         numberOfFailures3 <- sum(v <= underlinev)
         FirstFailures3 <- FirstFailures3 + (fcount >= 1)*1
         SomeFailures3 <- SomeFailures3 + (fcount >= 2)*1
         NumWave3 <- NumWave3 + fcount
         FirstWaveset3 <- FirstWaveset3 + length(wset)
         TotFailures3 <- TotFailures3 + numberOfFailures3

        }
        
        print(c)
        print(d)
        print(e)
        print(alpha)
        print(theta)
        
        Elliott$AvFirstFailures[c_counter, d_counter, e_counter, alpha_counter, theta_counter] <- FirstFailures1/iteration
        Elliott$AvSomeFailures[c_counter, d_counter, e_counter, alpha_counter, theta_counter] <- SomeFailures1/iteration
        Elliott$AvNumWave[c_counter, d_counter, e_counter, alpha_counter, theta_counter] <- NumWave1/iteration
        Elliott$AvFirstWaveset[c_counter, d_counter, e_counter, alpha_counter, theta_counter] <- FirstWaveset1/iteration
        Elliott$AvFailures[c_counter, d_counter, e_counter, alpha_counter, theta_counter] <- TotFailures1/iteration
        
        Mixed$AvFirstFailures[c_counter, d_counter, e_counter, alpha_counter, theta_counter] <- FirstFailures3/iteration
        Mixed$AvSomeFailures[c_counter, d_counter, e_counter, alpha_counter, theta_counter] <- SomeFailures3/iteration
        Mixed$AvNumWave[c_counter, d_counter, e_counter, alpha_counter, theta_counter] <- NumWave3/iteration
        Mixed$AvFirstWaveset[c_counter, d_counter, e_counter, alpha_counter, theta_counter] <- FirstWaveset3/iteration
        Mixed$AvFailures[c_counter, d_counter, e_counter, alpha_counter, theta_counter] <- TotFailures3/iteration
        
        }
      }
    }
  }
}

rm(tmp, tmp2)
rm(U, t, G, colSumG, L, C, hatC)
rm(Dnew, D, pold, p, pnew, total_assets,liquidation, port, seed, seeds)
rm(theta, theta_range, theta_counter, alpha, alpha_range, alpha_counter)
rm(e, e_range, e_counter, d, d_range, d_counter)
rm(fcount, zero, hero, iter, iteration)
```